\newif\ifhtml%
	\htmltrue%
	\htmlfalse%
\newif\ifiucr%
	\iucrtrue% figures according to iucr
%	\iucrfalse% figures normal
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\ifhtml%
	\documentclass[a4paper]{article}%
\else%
%	\documentclass[draft,s,preprint]{iucr}%
	\documentclass[s,preprint]{iucr}%
%	\documentclass[draft,s]{iucr}%
%	\documentclass[s]{iucr}%
		\paperprodcode{a000000}      % Replace with production code if known
		\paperref{xx9999}            % Replace xx9999 with reference code if known
		\papertype{FA}
		\paperlang{english}
		\journalcode{S}
		\journalyr{2009}
		\journaliss{1}
		\journalvol{65}
		\journalfirstpage{000}
		\journallastpage{000}
		\journalreceived{0 XXXXXXX 2009}
		\journalaccepted{0 XXXXXXX 2009}
		\journalonline{0 XXXXXXX 2009}
\fi%
%
\ifhtml % In case of web format output...
	\def\pgfsysdriver{pgfsys-tex4ht.def}
	\usepackage[caption=false,format=hang]{subfig}
	\usepackage[nolists]{endfloat}
	\usepackage[numbers,sort&compress]{natbib}
	\usepackage[disable]{todonotes}
		\renewcommand{\todo}[1]{\textcolor{red}{[TODO: #1]}} % redefines todo for html-conversion
%	\usepackage{changebar}
%		\nochangebars % disables changebars for html-conversion
\else
	\usepackage{todonotes}
%	\usepackage[pdftex,outerbars,color]{changebar}
%		\cbcolor{red}
%		\nochangebars
\fi
%
\usepackage[latin1]{inputenc} 						% so I can write my Name without \"{u}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{svn-multi}								% to add SVN-Versioning-Info
\let\Gray\relax
\usepackage[alsoload=binary,alsoload=synchem]{siunitx}		% typographically correct units (\milli\meter, \kilo\electronvolt), [alsoload=binary] > \SI{100}{\giga\byte}, [alsoload=synchem] > \SI{0.03}{\Molar}
\usepackage{multirow}								% multirows in tables
\usepackage{tikz} 									% extremely nice drawings
	\usetikzlibrary{patterns}
\usepackage{pgfplots} 								% ditto for plots
\usepackage{hyperref}
\usepackage{hypernat}

\newcommand{\imsize}{\linewidth}
\newlength\imagewidth % needed for scalebars
\newlength\imagescale % needed for scalebars

%% Subversion Information
\svnidlong
{$HeadURL: http://code.ana.unibe.ch/svn/WideFieldScanPaper/widefieldscan.tex $}
{$LastChangedDate: 2009-06-12 16:18:35 +0200 (Fr, 12 Jun 2009) $}
{$LastChangedRevision: 162 $}
{$LastChangedBy: $}

\ifhtml
	\DeclareGraphicsExtensions{.png}
	\newcommand{\footremember}[2]{\footnote{#2}\newcounter{#1}\setcounter{#1}{\value{footnote}}}%
	\newcommand{\footrecall}[1]{\footnotemark[\value{#1}]}%
\else
	\begin{document}
\fi
	
\title{Quality driven expansion of the field of view in synchrotron radiation x-ray tomographic microscopy}%
	
\ifhtml
	\author{David Haberthür\footremember{ana}{Institute of Anatomy, University of Bern, Switzerland}%
	  \and Christoph Hintermüller\footremember{psi}{Swiss Light Source, Paul Scherrer Institut, Villigen, Switzerland}%
	  \and Johannes C. Schittny\footrecall{ana}%
	  \and Marco Stampanoni\footrecall{psi} \footnote{Institute of Biomedical Engineering, University and ETH Zürich, Switzerland}%
	  }
	\begin{document}
	
	\maketitle
\else
\fi

\ifhtml
\else
	\shorttitle{A broader vision for tomographic microscopy}
	
	\cauthor[a]{David}{Haberthür}{haberthuer@ana.unibe.ch}{}
	\author[b]{Christoph}{Hintermüller}{}{}
	\author[a]{Johannes C.}{Schittny}{}{}
	\cauthor[b,c]{Marco}{Stampanoni}{marco.stampanoni@psi.ch}{}
	
	\aff[a]{Institute of Anatomy, University of Bern, \country{Switzerland}}
	\aff[b]{Swiss Light Source, Paul Scherrer Institut, \city{Villigen}, \country{Switzerland}}
	\aff[c]{Institute of Biomedical Engineering, University and ETH Zürich, \country{Switzerland}}
		
	\keyword{X-ray imaging}
	\keyword{computed tomography}
	\keyword{synchrotron microtomography}
	\keyword{SRXTM}
	\keyword{lung development}
	\keyword{alveoli}
	\keyword{acinus}
	
	\maketitle
\fi

\begin{abstract}
High resolution Volumetric data may be acquired at micrometer level within a few minutes using synchrotron radiation based X-ray tomographic microscopy (SRXTM). This speed enables us to investigate large objects at high resolution by combining several tomograms. The field of view may be increased in direction of the rotational axis of the sample by stacking single tomograms. In the present work we developed an acquisition protocol to increase the field of view perpendicular to the rotational axis, too. 3--5 high resolution tomograms were take side by side. The projectional images of each rotational angle were stitched to one large projection, followed by the generation of sinograms and the reconstruction of the entire sample volume. The total number of projectional images taken was optimized based on objective criteria taking reconstruction quality, scanning time and computing time into account. This method will be called wide field-SRXTM. Wide field-SRXTM increases the lateral field of view up to five times and the reconstructed sample volume up to 25-fold. We successfully applied it for the three-dimensional imaging of entire rat lung acini of an diameter of 3--4 mm at a resolution of less than \SI{2}{\micro\meter}.
\end{abstract}

\input{wfs-introduction}%
\input{wfs-materials-and-methods}%
\input{wfs-results}%
\input{wfs-discussion}%
\input{wfs-summary}%

\ifhtml
	\input{wfs-acknowledgements}%
	
	\bibliographystyle{unsrtnat}%
	\bibliography{../references}%
\else
	\ack{This work has been funded by grant \#3100A0-109874 of the Swiss National Science Foundation. We thank Mohammed Ouanella for excellent technical assistance with the preparation of the samples. Dr.\ Federica Marone, beamline scientist at TOMCAT, has been an expert help with the reconstructions. Dipl.-Ing.\ Sophie Rausch of the Institute for Computational Mechanics, Technische Universität München provided the lung sample shown in figure~\ref{fig:LungSlabSophie}.}%
%
\let\oldharvardurl=\harvardurl%
\renewcommand{\harvardurl}[1]{\relax}%
\referencelist[../references]%
\let\harvardurl=\oldharvardurl%
\fi

\end{document}