% !TEX root = widefieldscan.tex
\svnidlong
{$HeadURL$}
{$LastChangedDate$}
{$LastChangedRevision$}
{$LastChangedBy$}
%
\section{Summary and Outlook}\label{summary and outlook}

A method to increase the lateral field of view of tomographic imaging has been established. The method enables the high-resolution tomographic imaging of large samples---wider than the field of view of the imaging setup---in multiple steps, which are combined into an semi-automated tool chain. The enhanced field of view makes it possible to visualize entire acini inside rat lung samples, something which is not easily possible with the conventional tomographic setup present at TOMCAT and will be used for further examination of the mammalian terminal airway ends.

We have shown that an increase in the field of view of up to five times is feasible. Further increases of the field of view are limited only theoretically, but face problems with the amount of data to process. The dataset with a five-fold increase in field of view mentioned at the end of section~\ref{sec:Results} is composed of 1024 tiff files, each with a size of 4852$\times$4852 pixels, which adds up to a total size of nearly \SI{23}{\giga\byte}. Calculations and visualizations of datasets of this size require great optimizations of the processing queue and automation of calculations\todo{Should we mention the pending integration into beamline? $\rightarrow$ no intermediate stitched tiffs from MATLAB through direct stitching on cluster? $\rightarrow$ MS}.

Different optimized scanning protocols for covering a large field of view are provided for the end-users of the TOMCAT beamline. The end-user has the possibility to choose a suitable scanning protocol depending on a balance between acquisition time and expected reconstruction quality. Depending on this balance, we managed to reduce the image acquisition time down to \SI{16}{\percent} of the comparable gold standard scan, while keeping the quality of the reconstructed tomographic dataset on a level that still permitted automated segmentation of the lung structure and surrounding airspace, as shown in section~\ref{subsec:comparison}. The reduction in acquisition time reduces the time which the sample is irradiated and thus reduces the radiation dose inflicted on the sample. 

With this newly developed WF-SRXTM-method we have been able to acquire multiple datasets of the functional lung unit in the gas-exchange region of the terminal lung. These datasets are unrestricted by the FOV of the TOMCAT beamline and permit the automated segmentation of the airway-tissue-boundary due to the very high resolution and high image quality of the resulting tomographic reconstructions.